### 2023-11-01 about/vita.tex
Updates

Additive combinatorics, analytic number theory, random trees, analysis of algorithms.

@@

\begingroup\frenchspacing
\papercount=5
\pubbegin P
\papitem (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions.
{\sl Australasian Journal of Combinatorics}\/ {\bf 84},3 (2022), 357--374.
[arXiv:2106.05949]
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
{\sl Combinatorics, Probability and Computing}\/ {\bf 32},1 (2023), 68--90.
[arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science}\/ {\bf 24},1 (2022), \#7, 16~pp.
[arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl Random Structures and Algorithms}\/ {\bf 61},3 (2022), 520--542.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory}\/ {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

\sectheader{Submitted Papers}

\begingroup\parindent=10pt
\thing An uncertainty principle for M\"obius inversion on posets. {\sl arXiv:2302.02466} (2023), 7~pp.
\smallskip
\thing (with Jonah Saks)
On the homology of several number-theoretic set families. {\sl arXiv:2206.12535} (2022), 16~pp.
\endgroup
\endgroup%end the frenchspacing

@@

\sectheader{Research Experience}

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- June 2022}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal seminars, discussing
various topics related to branching
processes and other topics in probability and combinatorics.
(Gave a presentation at six of these: one on root estimation in Galton-Watson
trees, two on generating functions and elementary analytic combinatorics, two on graph regularity, and
one concerning two of Erd\H os's proofs on prime numbers.)

\medbreak
\leftright{\bf Sorting algorithms on manifolds}{\bf May -- August 2020}
\leftright{\sl Summer research project}{\sl McGill University}
\smallskip
Research project under the supervision of Michael Lipnowski.
Studied algorithms that investigate the topology of group actions on locally symmetric spaces.
Work involved writing of code in OCaml and PostScript that generates illustrations of certain quotient
spaces, in various models of hyperbolic geometry.
\medbreak

\leftright{\bf Interactive proofs}{\bf September -- December 2019}
\leftright{\sl Honours research project}{\sl McGill University}
\smallskip
Semester-long research project in the Computation and Logic Group, supervised
by Brigitte Pientka.
Proved a theorem in constructive logic concerning the formal verification
of the interactive proof assistant Harpoon and wrote OCaml code as part of
ongoing work on the functional programming language Beluga.
\medbreak

\leftright{\bf Bytecode compiler and interpreter}{\bf February -- June 2019}
\leftright{\sl Individual software project}{\sl Charles University}
\smallskip
Semester-long individual software project under the supervision of Adam Dingle.
Created OPythn, a bytecode compiler and virtual machine for a subset of Python.
OPythn includes support for lists, dictionaries, named and anonymous functions, objects, and classes.
It is implemented in OCaml using Ocamllex for lexing and Menhir for parsing.

@@

\starleftright{\bf After school care supervisor}{\bf January -- June 2023}
\leftright{\bf Suzuki Charter School}{\sl Edmonton, AB, Canada}
\smallskip
Supervised and facilitated activities (e.g., arts and crafts, soccer, board games, drawing/colouring, movie
days) for children in grades 1 through 6.
\medbreak

\starleftright{\bf Software developer}{\bf January -- May 2023}
\leftright{\bf Levven}{\sl Edmonton, AB, Canada}
\smallskip
Developed firmware for the manufacture and function of in-home IoT gateways, smart switches,
and related electronic products. Code primarily in \CEE\ and Python. Contributed to the open-source
Mongoose OS codebase.
\medbreak

\starleftright{\bf Visiting teaching assistant}{\bf July 2022}
\leftright{\bf Bocconi University}{\sl Como, CO, Italy}
\smallskip
Teaching assistant for a two-week summer school on random structures and combinatorial statistics,
which was
organised by Bocconi University in collaboration with Oxford University
and Imperial College London. Led problem sessions in the afternoons, with
around forty graduate-level students were in attendance.
\medbreak

\leftright{\bf Mentor}{\bf January -- April 2022}
\leftright{\bf Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Met with two undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting. Focused on topics in extremal combinatorics related to the increasing
triples problem, as well as topics related to Khovanskii's theorem.
\medbreak

@@

\begingroup\frenchspacing
\fictioncount=3
\pubbegin F
\ficitem ``Senang Diri,'' {\sl Existere} {\bf 42},2 (2023), 17--25.
\ficitem ``The Vigil,'' {\sl Ricepaper Magazine} (2023), online.
\ficitem ``Mountain Pass,'' {\sl Prairie Journal of Canadian Literature} {\bf 79} (2023), 48--55.
\endgroup%end the frenchspacing

@@

{\bf Programming Languages}\par
\CEE, OCaml, Python, Java, PostScript, Haskell, Scheme Lisp,  Standard ML, {\tt CWEB}, {\tt MIXAL}, MIPS Assembly.
\medbreak

>>>>

Additive combinatorics, enumerative combinatorics, analysis of random discrete structures.

@@

\begingroup\frenchspacing
\papercount=6
\pubbegin P
\papitem (with Jonah Saks)
On the homology of several number-theoretic set families. To appear in
{\sl Enumerative Combinatorics and Applications} (2024), 17~pp.
[arXiv:2206.12535]
\papitem (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions.
{\sl Australasian Journal of Combinatorics}\/ {\bf 84},3 (2022), 357--374.
[arXiv:2106.05949]
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
{\sl Combinatorics, Probability and Computing}\/ {\bf 32},1 (2023), 68--90.
[arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science}\/ {\bf 24},1 (2022), \#7, 16~pp.
[arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl Random Structures and Algorithms}\/ {\bf 61},3 (2022), 520--542.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory}\/ {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\goodbreak

\fictioncount=3
\pubbegin F
\ficitem ``Senang Diri,'' {\sl Existere} {\bf 42},2 (2023), 17--25.
\ficitem ``The Vigil,'' {\sl Ricepaper Magazine} (2023), online.
\ficitem ``Mountain Pass,'' {\sl Prairie Journal of Canadian Literature} {\bf 79} (2023), 48--55.
\endgroup%end the frenchspacing

@@

\starleftright{\bf After school care supervisor}{\bf January -- June 2023}
\leftright{\sl Suzuki Charter School}{\sl Edmonton, AB, Canada}
\smallskip
Supervised and facilitated activities (e.g., arts and crafts, soccer, board games, drawing/colouring, movie
days) for children in grades 1 through 6.
\medbreak

\starleftright{\bf Software developer}{\bf January -- May 2023}
\leftright{\sl Levven}{\sl Edmonton, AB, Canada}
\smallskip
Developed firmware for the manufacture and function of in-home IoT gateways, smart switches,
and related electronic products. Code primarily in \CEE\ and Python. Contributed to the open-source
Mongoose OS codebase.
\medbreak

\starleftright{\bf Visiting teaching assistant}{\bf July 2022}
\leftright{\sl Bocconi University}{\sl Como, CO, Italy}
\smallskip
Teaching assistant for a two-week summer school on random structures and combinatorial statistics,
which was
organised by Bocconi University in collaboration with Oxford University
and Imperial College London. Led problem sessions in the afternoons, with
around forty graduate-level students were in attendance.
\medbreak

\leftright{\bf DRP Mentor}{\bf January -- April 2022}
\leftright{\sl Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Met with two undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting. Focused on topics in extremal combinatorics related to the increasing
triples problem, as well as topics related to Khovanskii's theorem.
\medbreak

@@

@@

{\bf Programming Languages}\par
\CEE, OCaml, Python, Java, PostScript, Haskell, Scheme Lisp,  Standard ML, {\tt CWEB}, {\tt MIXAL},
{\mc MIPS} Assembly.
\medbreak

### 2023-11-01 misc/expo/kelleymeka.tex
Updates

\maketitle{Kelley and Meka's proof of Roth's theorem}{by}{Marcel K. Goh}{23 August 2023}

@@

\edef\holderlifting{\the\thmcount}
\parenproclaim Lemma~{\advthm} (H\"older lifting). Let $\eps\ge 0$ and let $A$ and $C$ be subsets of
a finite abelian group $G$, where $C$ has relative density $\gamma$. Then at least one of
the following two statements holds.
\medskip
\item{i)} $\bigl|\langle \mu_A *\mu_A, \mu_C\rangle - 1\bigr| \le \eps$
\smallskip
\item{ii)} $\norm{\mu_A\circ \mu_A - 1}_p \ge \eps/2$ for some $p = O\bigl(\log(1/\gamma)\bigr)$.

@@

This lemma tells us that if $\langle \mu_A*\mu_A,\mu_C\rangle \ge 1/2$, then $\norm{\mu\circ \mu_A-1}_p \ge 1/4$
for some $p = O\bigl(\log(1/\gamma)\bigr)$. This information can then be fed to the following general lemma.

@@

\bignorm{(\mu_A\circ \mu_A)^p, f}_{p(\mu)}^p

@@

\ex_{s\in G^p} \indic{\alpha_1(s)\alpha_2<M^2} \alpha_1(s)\alpha_2(s)

@@

\proof Let $p'$ be the smallest even integer at least $p+\eps^{-1}\log(\delta^{-1})$.
By the previous lemma applied to the set
$\one_{G\setminus S}$, there exist sets $A_1\subseteq B_1$ and $A_2\subseteq B_2$ with densities
satisfying
$$\eqalign{
\min\bigl\{\mu_{B_1}(A_1), \mu_{B_2}(A_2)\bigr\} &\ge
{1\over 4} \alpha^{2p'} \norm{\mu_A\circ\mu_A}_{p'(\mu)}^{2p'}  \cr
&\ge {1\over 4}\bigl(\alpha\norm{\mu_A\circ\mu_A}_{p(\mu)}\bigr)^{2p+2\eps^{-1}\log(\delta^{-1})+O(1)} \cr
&= \Omega\bigl( (\alpha \norm{\mu_A\circ\mu_A}_{p(\mu)})^{2p+O(\eps^{-1}\log(\delta^{-1}))}\bigr)\cr
}$$
such that
$$\langle \mu_{A_1}\circ\mu_{A_2}, \one_{G\setminus S}\rangle
\le {\bigl\langle (\mu_A\circ\mu_A)^{p'}, \one_{G\setminus S}\bigr\rangle_{\mu} \over
\norm{\mu_A\circ\mu_A}^{p'}_{p'(\mu)}}.$$
Our construction of $S$ ensures that
$${\bigl\langle (\mu_A\circ\mu_A)^{p'}, \one_{G\setminus S}\bigr\rangle_{\mu} \over
\norm{\mu_A\circ\mu_A}^{p'}_{p'(\mu)}} \le (1-\eps)^{p'},$$
and since $p'\ge \eps^{-1}\log(\delta^{-1})$, we have
$$(1-\eps)^{p'}\le e^{-\eps p'} \le \delta.$$
Putting everything together, we have
$$\langle \mu_{A_1}\circ\mu_{A_2}, \one_{G\setminus S}\rangle \le \delta,$$
so that
$$\langle \mu_{A_1}\circ\mu_{A_2}, \one_S\rangle
= 1- \langle \mu_{A_1}\circ\mu_{A_2}, \one_{G\setminus S}\rangle \ge 1-\delta,$$
which completes the proof.\slug

>>>>

\maketitle{Kelley and Meka's proof of Roth's theorem}{by}{Marcel K. Goh}{12 October 2023}

@@

\edef\holderlifting{\the\thmcount}
\parenproclaim Lemma~{\advthm} (H\"older lifting). Let $\eps\ge 0$ and let $A$ and $C$ be subsets of
a finite abelian group $G$, where $C$ has relative density at least $\gamma$. Then at least one of
the following two statements holds.
\medskip
\item{i)} $\bigl|\langle \mu_A *\mu_A, \mu_C\rangle - 1\bigr| \le \eps$
\smallskip
\item{ii)} $\norm{\mu_A\circ \mu_A - 1}_p \ge \eps/2$ for some $p = O\bigl(\log(1/\gamma)\bigr)$.

@@

This lemma tells us that if $\langle \mu_A*\mu_A,\mu_C\rangle \ge 1/2$, then
$\norm{\mu_A\circ \mu_A-1}_p \ge 1/4$
for some $p = O\bigl(\log(1/\gamma)\bigr)$. This information can then be fed to the following general lemma.

@@

\bignorm{\mu_A\circ \mu_A}_{p(\mu)}^p

@@

\ex_{s\in G^p} \indic{\alpha_1(s)\alpha_2(s)<M^2} \alpha_1(s)\alpha_2(s)

@@

\proof Let $p'$ be the smallest even integer at least $p+\eps^{-1}\log(\delta^{-1})$.
By the previous lemma applied to the function
$\one_{G\setminus S}$, there exist sets $A_1\subseteq B_1$ and $A_2\subseteq B_2$ with densities
satisfying
$$\eqalign{
\min\bigl\{\mu_{B_1}(A_1), \mu_{B_2}(A_2)\bigr\} &\ge
{1\over 4} \alpha^{2p'} \norm{\mu_A\circ\mu_A}_{p'(\mu)}^{2p'}  \cr
&\ge {1\over 4}\bigl(\alpha\norm{\mu_A\circ\mu_A}_{p(\mu)}\bigr)^{2p+2\eps^{-1}\log(\delta^{-1})+O(1)} \cr
&= \Omega\bigl( (\alpha \norm{\mu_A\circ\mu_A}_{p(\mu)})^{2p+O(\eps^{-1}\log(\delta^{-1}))}\bigr)\cr
}$$
such that
$$\langle \mu_{A_1}\circ\mu_{A_2}, \one_{G\setminus S}\rangle
\le {\bigl\langle (\mu_A\circ\mu_A)^{p'}, \one_{G\setminus S}\bigr\rangle_{\mu} \over
\norm{\mu_A\circ\mu_A}^{p'}_{p'(\mu)}}.$$
Our construction of $S$ ensures that
$${\bigl\langle (\mu_A\circ\mu_A)^{p'}, \one_{G\setminus S}\bigr\rangle_{\mu} \over
\norm{\mu_A\circ\mu_A}^{p'}_{p'(\mu)}} \le (1-\eps)^{p'},$$
and since $p'\ge \eps^{-1}\log(\delta^{-1})$, we have
$$(1-\eps)^{p'}\le e^{-\eps p'} \le \delta.$$
Putting everything together, we have
$$\langle \mu_{A_1}\circ\mu_{A_2}, \one_{G\setminus S}\rangle \le \delta,$$
so that
$$\langle \mu_{A_1}\circ\mu_{A_2}, \one_S\rangle
= 1- \langle \mu_{A_1}\circ\mu_{A_2}, \one_{G\setminus S}\rangle \ge 1-\delta,$$
which completes the proof.\slug
